### 2016-12-22 Plos-one-manuscript/latex/manuscript.tex
spell check

%range of 226 ul, one tip size per pipette

@@

Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
A 1 mL or 3 mL BD syringe twists to lock in the body part and is held into place by the syringe flanges.
The 30-300 uL configuration uses a 1 mL pipette and the 100-1000 uL configuration uses a 3 mL pipette.
The plunger part slides freely in the body part and actuates the syringe by pushing the thumb press. 
The pipette is spring loaded towards a set point which is adjustable by a set-screw. 
When the plunger is depressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
The plunger is held in place with a latching button design which is released with a lever drawing in fluid.
The displacement is equal to the distance between the set position and the latched position.
The pipette can also be pressed past the latched position to 'blow-out' the transfered fluid completely from the pipette tip.   
Additional materials required for assembly include a spring, a nut and bolt and washers.
Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
Instead a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
Our printed pipette mimics commercial pipettes's design, function, and user operation, making it intuitive to use.
Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.

@@

A small amount of parrifin wax is applyed to the screw to prevent slop from causeting the set point to drift after each acuation.
The nut is sunk in to the hex inset in the body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.

@@

\begin{figure}
\caption{
{\bf CAD renderings of assembled pipette and function.} The pipetted actuates the syringe to three positions. {\bf(i) The set position.} The position of the screw determines the total displacement. The pipette is spring loaded to return to this position {\bf (ii) The latched position.} When the plunger is pressed the pipette locks at this position. The tip is then placed in a liquid and the button pressed to release the pipette back to the set position, drawing in liquid. {\bf (iii) The blow-out position.} The fluid is transfered by pressing the plunger past the latched position to blow-out all the liquid.  
}
\label{fig1}
\end{figure}

@@

\subsection*{Validation}
The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
Data was taken for printed pipettes with existing graduations as well as with the adjusted scale.
The commerical pipette was adjusted to the desired volume and 5 transfers were taken.
The systematic error and random error was calculated according to ISO 8655 (Table~\ref{table3,table4}).

@@

This pipette improves on existing open design pipettes in several ways. 
Most significatly the user is able to adjust the syringe accuratly without verifying the volume with a scale.
In additon the assembly requires no permanent connections using tape or glue which allows for re-configurationorn and easy replacment of parts.
Our pipette is able to transfer from the bottom of a 15 mL conical tube which is a requirement for many routine lab procedures such as aspirating supernatant from a centrifuged cell pellet.
This design does not use a membrane that may wear out and require tedious replacement.

The only major limitation of this design compared to the briopipette is the option for a pipette tip ejector, although incorporation of a similar design in our pipette would not leave room for it to reach into a 15 mL conical tube. 
Our pipette requires a syringe and some additional hardware where briopipette's additional parts can be obtained virtually anywhere.
The briopipette also allows step-wise shifts in displacement allowing the user to quickly change to a relative volume

>>>>

%range of 226 uL, one tip size per pipette

@@

Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
The 30-300 uL configuration uses a 1 mL pipette and the 100-1000 uL configuration uses a 3 mL pipette.
The plunger part slides freely in the body part and actuates the syringe by pushing the thumb press. 
The pipette is spring loaded towards a set point which is adjustable by a set-screw. 
When the plunger is depressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
The plunger is held in place with a latching button design which is released with a lever drawing in fluid.
The displacement is equal to the distance between the set position and the latched position.
The pipette can also be pressed past the latched position to 'blow-out' the transferred fluid completely from the pipette tip.   
Additional materials required for assembly include a spring, a nut and bolt and washers.
Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
Instead a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.
Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.

@@

A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
The nut is sunk in to the hex inset in the body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.

@@

\begin{figure}
\caption{
{\bf CAD renderings of assembled pipette and function.} The pipetted actuates the syringe to three positions. {\bf(i) The set position.} The position of the screw determines the total displacement. The pipette is spring loaded to return to this position {\bf (ii) The latched position.} When the plunger is pressed the pipette locks at this position. The tip is then placed in a liquid and the button pressed to release the pipette back to the set position, drawing in liquid. {\bf (iii) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.  
}
\label{fig1}
\end{figure}

@@

\subsection*{Validation}
The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
The printed pipette was adjusted to the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
Data was taken for printed pipettes with existing graduations as well as with the adjusted scale.
The commercial pipette was adjusted to the desired volume and 5 transfers were taken.
The systematic error and random error was calculated according to ISO 8655 (Table~\ref{table3,table4}).

@@

This pipette improves on existing open design pipettes in several ways. 
Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
In addition the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
Our pipette is able to transfer from the bottom of a 15 mL conical tube which is a requirement for many routine lab procedures such as aspirating supernatant from a centrifuged cell pellet.
This design does not use a membrane that may wear out and require tedious replacement.

The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector, although incorporation of a similar design in our pipette would not leave room for it to reach into a 15 mL conical tube. 
Our pipette requires a syringe and some additional hardware where biropipette's additional parts can be obtained virtually anywhere.
The biropipette also allows step-wise shifts in displacement allowing the user to quickly change to a relative volume
